---
title: "FNCE611 Problem Set 4"
author: "Jessica Blum, Jordan Farrer, Marc Lanthemann"
date: '2017-03-24'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    number_sections: yes
    toc: false
  bookdown::html_document2:
    css: style.css
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = 'center', size = 'small', fig.pos = 'H',
                      fig.width = 6, fig.height = 3.5)

knitr::knit_hooks$set(
          size = function(before, options, envir) {
                  if (before) return(paste0("\n \\", options$size, "\n\n"))
                  else return("\n\n \\normalsize \n")
                  }
          , inline = function(x) {if(!is.numeric(x)){ x }else{ prettyNum(round(x,4), big.mark=",") } }
          )
```

```{r report-load-packages, results = 'hide', include = FALSE}
pacman::p_load(tidyverse, forcats, pander, stringr, lubridate, ggrepel, extrafont, jrfTools, broom)
```

```{r report-additional-setup, include = FALSE}
options(scipen = 999)
panderOptions('digits', 8)
panderOptions('round', 4)
panderOptions('keep.trailing.zeros', TRUE)
```

# Question 1

```{r}
dell_data <- read_csv("fnce611_hw4.csv")
```

## a)

```{r}
lm1 <- lm(dell_excess_return ~ sp_excess_return, data = dell_data)

equation = function(x) {
  lm_coef <- list(a = formatC(coef(x)[1], digits = 4, format = 'f'),
                  b = formatC(coef(x)[2], digits = 4, format = 'f'),
                  r2 = formatC(summary(x)$r.squared, digits = 2, format = 'f'));
  lm_eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(R)^2~"="~r2,lm_coef)
  as.character(as.expression(lm_eq));                 
}

dell_data %>%
  ggplot(aes(x = sp_excess_return, y = dell_excess_return)) +
  geom_point() + 
  geom_smooth(method = 'lm', se = FALSE) +
  annotate("rect", xmin = -.17, xmax = -.028, ymin = .08, ymax = 0.12, fill="white", colour = pal538[['red']]) +
  annotate("text", x = -0.1, y = 0.1, label = equation(lm1), parse = TRUE, 
           family = "DecimaMonoPro", size = 3) +
  theme_jrf(users_v = 'rstudio') +
  labs(title = "Linear Regression of 5-year History", x = "S&P Excess Return", 
       y = "Dell Excess Return")
```


```{r}
beta <- 
  lm1 %>% 
  tidy() %>%
  filter(term == "sp_excess_return") %>%
  select(estimate) %>%
  unlist() %>%
  unname()
```

We find that $\beta = `r beta`$.

## b)

```{r}
dell_expected_return <- mean(dell_data$risk_free_return) * 52 + 
        beta * (mean(dell_data$sp_return) * 52 - mean(dell_data$risk_free_return) * 52)
```

Dell's expected return is `r dell_expected_return`.

## c)

\begin{align}
\ r_{dell} & = r_{f} + \beta_{dell}(r_{m} + r_{f}) \\
 & = 0.0387 + `r beta` (0.0845 - 0.0387) \\
 & = `r 0.0387 + beta * (0.0845 - 0.0387)`
\end{align}


+ Pros:
+ Cons:

## d)

```{r}
variance <- 
  dell_data %>%
  summarise(
    dell_var = sd(dell_return)^2 * 52
    , sp_var = sd(sp_return)^2 * 52
    )
```


```{r echo = FALSE}
variance %>%
  pander(caption = "Annualized Variance of Dell and the market return")
```

## e)

\begin{align}
\ Var(r_{dell}) &= \beta_{dell}^2 Var(r_{m}) + [\textnormal{firm specific risk}] \\
\ `r variance$dell_var` &= `r beta`^2 \cdot `r variance$sp_var` + [\textnormal{firm specific risk}]
\end{align}

Of Dell's sample variance, **`r variance$dell_var`**, we can say that **`r beta^2 * variance$sp_var`** is from market risk and **`r variance$dell_var - beta^2 * variance$sp_var`** is firm specific risk.

# Question 2


# Question 3


# Question 4
